### 2021-06-08 paper/report.tex
New results.
Improve equations.

\begin{align*}
    x &= \frac{nnewlyinfected \times shareknowncases \times P(PCR | S)}{nsymptomaticanduntested} \\
    y &= \frac{nnewlyinfected \times shareknowncases \times P(PCR | S)}{nasymptoptomaticandinfectedanduntested} \\
    z &= \frac{P(PCR | RT)}{survey}
\end{align*}

@@

Modelling a population of agents according to actual demographic characteristics means
that we can use a wide array of data to identify and estimate the model's many
parameters.\footnote{See section S.X of the supplementary materials for an
overview.}\comment[id=HM]{Need to make a list including symbols, maybe you can fetch the
parameters from the model and then we brainstorm re notation?} Mobility data is used to
model the reductions in work contacts. School and daycare policies are incorporated
directly from official directives. Infection rates by age and geographical region are
estimated to match to officially recorded numbers; so is the prevalence of virus
strains. In order to translate simulated cases in our model to officially recorded
cases, we use the model depicted in Figure~\ref{fig:model_for_official_cases}.
\comment[id=HM]{Add a sentence.} A further advantage is that the simulated data have a
structure that resembles datasets used for regression models, which allows additional
plausibility checks by re-running the same models on the model-generated
data.\comment[id=HM]{Only keep if we actually do something like that.}

@@

        \caption{{\small Tests and vaccinations}}
        \label{fig:antigen_tests_vaccinations}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/share_of_b117_acc_to_rki}

        \caption{Fraction of B.1.1.7 strain among measured infections}

        \textcolor{red}{We'll have this compared to our baseline simulation in the next
        iteration.}
        \label{fig:share_b117}
    \end{subfigure}

>>>>

\begin{align*}
    x &= \frac{n\_newly\_infected \times share\_known\_cases \times P(PCR | S)}{n\_symptomatic\_and\_untested} \\
    y &= \frac{n\_newly\_infected \times share\_known\_cases \times P(PCR | S)}{n\_asymptoptomatic\_and\_infected\_and\_untested} \\
    z &= \frac{P(PCR | RT)}{survey}
\end{align*}

@@

Modelling a population of agents according to actual demographic characteristics means
that we can use a wide array of data to identify and estimate the model's many
parameters.\footnote{See section S.X of the supplementary materials for an
overview.}\comment[id=HM]{Need to make a list including symbols, maybe you can fetch the
parameters from the model and then we brainstorm re notation?} Mobility data is used to
model the reductions in work contacts. School and daycare policies are incorporated
directly from official directives. Infection rates by age and geographical region are
estimated to match to officially recorded numbers; so is the prevalence of virus strains.
In order to translate simulated cases in our model to officially recorded cases, we use
the model depicted in Figure~\ref{fig:model_for_official_cases}.\comment[id=HM]{Add a
sentence.} A further advantage is that the simulated data have a structure that resembles
datasets used for regression models, which allows additional plausibility checks by
re-running the same models on the model-generated data.\comment[id=HM]{Only keep if we
actually do something like that.}

@@

        \caption{{\small Tests and vaccinations}}
        \label{fig:antigen_tests_vaccinations}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_share_b117}

        \caption{Fraction of B.1.1.7 strain among measured infections}
        \label{fig:share_b117}
    \end{subfigure}
